\documentclass[11pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\itshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  Sam C. Levin - CV }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Sam C. Levin:  CV (Curriculum Vitae)},
            pdfauthor={Sam C. Levin},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

\begin{document}


\centerline{\huge \bf Sam C. Levin}

\vspace{2 mm}

\hrule

\vspace{2 mm}


\moveleft.5\hoffset\centerline{German Centre for Integrative Biodiversity, Deutscherplatz 5e, Leipzig,
Germany}
\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:levisc8@gmail.com}{\nolinkurl{levisc8@gmail.com}}} \hspace{1 mm}  \faGithub \hspace{1 mm} \href{http://github.com/levisc8}{\tt levisc8} \hspace{1 mm}   \faTwitter \hspace{1 mm} \href{https:/twitter.com/SamLevin5}{\tt SamLevin5} \hspace{1 mm}    | \emph{Updated:} \today}

\vspace{2 mm}

\hrule


\hypertarget{education}{%
\section{Education}\label{education}}

\emph{Martin Luther University Halle-Wittenberg}

PhD Biology \hfill 2018-Present

\emph{Martin Luther University Halle-Wittenberg}

MSc Biology \hfill 2016-2017

\emph{Wake Forest University}

BA Biology \hfill 2008-2012

\hypertarget{work-experience}{%
\section{Work Experience}\label{work-experience}}

\emph{Martin Luther University Halle-Wittenberg}

Research Officer \hfill 2018-Present

\emph{Helmholtz-Zentrum für Umweltforschung }

Student Research Assistant \hfill 2017

\emph{German Centre for Integrative Biodiversity}

Student Research Assistant \hfill 2016 - 2018

\emph{University of Missouri-St.~Louis}

Field Research Technician \hfill 2015 - 2016

\emph{Washington University in St.~Louis}

Field Research Technician \hfill 2014 - 2015

\emph{Student Conservation Association}

National Park Service Southeast EPMT Intern \hfill 2013 - 2014

\hypertarget{research-interests}{%
\section{Research Interests}\label{research-interests}}

\textbf{Invasions}: understanding how demography, phylogeny, and
functional traits interact to determine who becomes invasive and who
remains benign.

\textbf{Software Development}: creating open source tools for
researchers to efficiently analyze, publish, and share their data.

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{journal-articles}{%
\subsection{Journal Articles}\label{journal-articles}}

\(^\ast\) \emph{denotes mentee}

\textbf{Levin SC}, Crandall RM, Pokoski TC\(^\ast\), Stein \& Knight TM
(2020). Phylogenetic and functional distinctiveness explain alien plant
population responses to competition. Proceedings of the Royal Society B.
287: 20201070. DOI: 10.1098/rspb.2020.1070

Sandel B, Weigelt P, Kreft H, Keppel G, van der Sande MT, \textbf{Levin
SC}, Smith S, Craven DC \& Knight TM (2019). Current climate, isolation,
and history drive global patterns of tree phylogenetic endemism. Global
Ecology and Biogeography. DOI: 10.1111/geb.13001

Compagnoni A, Bibian BJ, Ochocki BM, \textbf{Levin SC}, Zhu K \& Miller
TEX (2019). popler: an R package for extraction and synthesis of
population time series from the long-term ecological research (LTER)
network. Methods in Ecology and Evolution. DOI: 10.1111/2041-210X.13319

\textbf{Levin SC}, Crandall RM, Knight TM (2019) Population projection
models for 14 alien plant species in the presence and absence of
above‐ground competition. Ecology. DOI:
\url{https://doi.org/10.1002/ecy.2681}

Carl G, \textbf{Levin SC}, Kühn I. (2018) spind: an R Package to Account
for Spatial Autocorrelation in the Analysis of Lattice Data.
Biodiversity Data Journal. 6: e20760. DOI:
\url{https://doi.org/10.3897/BDJ.6.e20760}

\hypertarget{workshops-invited-talks}{%
\subsection{Workshops \& Invited Talks}\label{workshops-invited-talks}}

\textbf{Levin SC}. Invasive plants: research, control, and what you can
do to help! Point Reyes National Park, May 2020. (Cancelled due to
COVID-19 pandemic).

\textbf{Levin SC} \& Salguero-Gomez R. Effective, efficient, and safe
data collection with UAVs. Oxford University, January 2020.

Salguero-Gomez R, Jones OR, \emph{et al.} A gentle introduction to the
COMADRE \& COMPADRE databases for demographic analyses. British
Ecological Society, Belfast, December 2019.

\hypertarget{presentations}{%
\subsection{Presentations}\label{presentations}}

\(^\ast\) \emph{denotes mentee; \(^\#\) denotes poster presentations,
otherwise oral}

\textbf{2018}

\textbf{Levin SC}, RM Crandall, TC Pokoski, Stein C, Knight TM.
Mechanisms underlying the differential success of alien plant species.
Ecological Society of America -- New Orleans, USA

\textbf{2016}

\textbf{Levin SC}, Stein C, Knight TM. Phylogenetic novelty alters the
strength of biotic interactions for exotic plant species. NeoBiota 2016
-- Vianden, Luxembourg

\textbf{Levin SC}, Stein C, Knight TM. Phylogenetic novelty alters the
strength of biotic interactions for exotic plant species. iDiv
Conference -- Leipzig, Germany

\textbf{2015}

Poor E\(^\ast\),Thompson AH\(^\ast\), \textbf{Levin SC}, Knight TM.
Novel functional traits aid the success of the invasive biennial Carduus
nutans. Washington University in St.~Louis Undergraduate Research
Symposium -- St.~Louis, MO \(^\#\)

Workman M\(^\ast\), Thompson AH\(^\ast\), \textbf{Levin SC}, Knight TM.
Competitive release may increase the fitness of exotic plants in their
novel range. Washington University in St.~Louis Undergraduate Research
Symposium -- St.~Louis, MO \(^\#\)

\textbf{2014}

Patterson A\(^\ast\), Galluppi CG, \textbf{Levin SC}, Maynard EE, Knight
TM. How plant species become common: examining the success strategies of
native and invasive plants. Washington University in St.~Louis
Undergraduate Research Symposium -- St.~Louis, MO \(^\#\)

Van Horn T\(^\ast\), Galluppi CG, \textbf{Levin SC}, Knight TM.
Examining the enemy release hypothesis in Ozark woody species.
Washington University in St.~Louis Undergraduate Research Symposium --
St.~Louis, MO \(^\#\)

\hypertarget{software}{%
\section{Software}\label{software}}

Maintainer (current) and developer (\textgreater{} v2.0.0) of
\emph{spind}.
\href{https://cran.r-project.org/web/checks/check_results_spind.html}{CRAN}
and \href{https://github.com/levisc8/spind}{Github}

Maintainer and developer of \emph{ipmr}.
\href{https://levisc8.github.io/ipmr/}{Project page}

Maintainer and developer of the \emph{Padrino IPM Database} and
\emph{Rpadrino}. \href{https://github.com/levisc8/RPadrino}{Project
page}

Contributed to development of
\href{https://github.com/AldoCompagnoni/popler}{popler},
\href{https://github.com/iainmstott/popdemo}{popdemo},
\href{https://github.com/jonesor/Rcompadre}{Rcompadre}, and
\href{https://github.com/jonesor/Rage}{Rage}.

\hypertarget{languages}{%
\section{Languages}\label{languages}}

Fluent in English and R, proficient with Stan, Git, and C++, and
familiar with Python and German.

\hypertarget{certifications}{%
\section{Certifications}\label{certifications}}

United States FAA Part 107 UAV Pilot License

United States NPS S212 A Faller

\hypertarget{mentoring}{%
\section{Mentoring}\label{mentoring}}

Ana Bogdan \hfill Babe\c s-Bolyai University, Cluj-Napoca, Romania

Tyler Pokoski \hfill  University of Iowa 2017

Tom Collins \hfill Missouri S\&T 2017

Amy Patterson \hfill Washington University in St.~Louis 2015

Amibeth Thompson \hfill Illinois College 2014

Sami Hunkler \hfill University of California, Berkeley 2017

Thomas Van Horn \hfill Washington University in St.~Louis 2018

Sarah Link \hfill Eureka High School 2015

Brenda Alvarado \hfill Francis Howell North 2015

Matilda Workman \hfill Kirkwood High School 2017

Elizabeth Poor \hfill Clayton High School 2017

\hypertarget{service}{%
\section{Service}\label{service}}

Reviewer for rOpenSci, BMC Ecology, Annals of Botany, and Plant Ecology

\hypertarget{referees}{%
\section{Referees}\label{referees}}

\textbf{Dr.~Tiffany Knight}

Martin Luther University, Helmholtz-Zentrum für Umweltforschung, German
Centre for Integrative Biodiversity

\href{mailto:tiffany.knight@idiv.de}{\nolinkurl{tiffany.knight@idiv.de}}

\textbf{Dr.~Roberto Salguero-Gomez}

Oxford University Department of Zoology

\href{mailto:rob.salguero@zoo.ox.ac.uk}{\nolinkurl{rob.salguero@zoo.ox.ac.uk}}

\end{document}
