\documentclass[11pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\itshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  Sam C. Levin - CV }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Sam C. Levin:  CV (Curriculum Vitae)},
            pdfauthor={Sam C. Levin},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

\begin{document}


\centerline{\huge \bf Sam C. Levin}

\vspace{2 mm}

\hrule

\vspace{2 mm}


\moveleft.5\hoffset\centerline{German Centre for Integrative
Biodiversity, Deutscherplatz 5e, Leipzig, Germany}
\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:levisc8@gmail.com}{\nolinkurl{levisc8@gmail.com}}} \hspace{1 mm}  \faGithub \hspace{1 mm} \href{http://github.com/levisc8}{\tt levisc8} \hspace{1 mm}   \faTwitter \hspace{1 mm} \href{https:/twitter.com/SamLevin5}{\tt SamLevin5} \hspace{1 mm}    | \emph{Updated:} \today}

\vspace{2 mm}

\hrule


\hypertarget{education}{%
\section{Education}\label{education}}

\emph{Martin Luther University Halle-Wittenberg}

PhD Biology \hfill 02/2018-Present

\emph{Martin Luther University Halle-Wittenberg}

MSc Biology \hfill 04/2016-12/2017

\emph{Wake Forest University}

BA Biology \hfill 08/2008-05/2012

\hypertarget{work-experience}{%
\section{Work Experience}\label{work-experience}}

\textbf{Martin Luther University Halle-Wittenberg}

\emph{Research Officer}

02/2018-Present

26h/week

\$34,000/Year

\begin{itemize}
\item
  Designed and carried out data collection for \emph{Carpobrotus}
  species across 6 countries and 23 field sites in their native and
  invaded ranges using novel, drone based methodology.
\item
  Analyzed drone data using R and C++ programming languages to connect
  environmental covariates to population dynamics for inference on areas
  at risk for future invasion under different climate scenarios.
\item
  Designed and implemented an R package, \texttt{ipmr}, for flexibly
  developing Integral Projection Models in the R programming language.
\item
  Designed and implemented a database, \texttt{PADRINO}, to re-build
  published Integral Projection Models to address synthetic questions in
  ecology and evolutionary biology.
\end{itemize}

\textbf{Helmholtz-Zentrum für Umweltforschung}

\emph{Student Research Assistant}

05/2017

10h/week

\$10,560/Year

\textbf{German Centre for Integrative Biodiversity}

\emph{Student Research Assistant}

07/2016 - 01/2018

20h/week

\$10,560/Year

\textbf{University of Missouri-St.~Louis} \emph{Field Research
Technician} 11/2015 - 03/2016\\
37.5h/week \$33,000/Year

\textbf{Washington University in St.~Louis} \emph{Field Research
Technician} 04/2014 - 10/2015 37.5h/week \$33,000/Year

\textbf{Student Conservation Association} \emph{National Park Service
Southeast EPMT Intern} 09/2013 - 04/2014 40h/week \$10,000/Year

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{journal-articles}{%
\subsection{Journal Articles}\label{journal-articles}}

\(^\ast\) \emph{denotes mentee}

\textbf{Levin SC}, Evers S\(^\ast\), Pena-Guerrero M, Compagnoni AC,
Childs DZ, Knight TM \& Salguero-Gomez R (\emph{in prep}). Padrino: An
open access database of Integral Projection Models.

Keppel G, Craven D, Weigelt P, Smith SA, van der Sande MT, Sandel B,
\textbf{Levin SC}, Kreft H \& Knight TM (2021). Synthesizing tree
biodiversity data to understand global patterns and processes of
vegetation. Journal of Vegetation Science. DOI: 10.1111/jvs.13021

\textbf{Levin SC}, Childs DZ, Compagnoni AC, Evers S\(^\ast\), Knight TM
\& Salguero-Gomez R (\emph{in review} at \emph{Methods in Ecology and
Evolution}). ipmr: Flexibly implement Integral Projection Models in R.

Bogdan A\(^\ast\), \textbf{Levin SC}, Salguero-Gomez R \& Knight TM.
(2021). Demographic analysis of an Israeli \emph{Carpobrotus}
population. Plos One. DOI: 10.1371/journal.pone.0250879.

Paniw M, James T, Archer CR, Romer G, \textbf{Levin SC}, Compagnoni AC,
\emph{et al.} (2021). Global analysis reveals complex demographic
responses of mammals to climate change. Journal of Animal Ecology. DOI:
10.1111/1365-2656.13467

Compagnoni AC, \textbf{Levin SC}, Childs DZ, Harpole S, Paniw M, Romer
G, \emph{et al.} (2021). Short-lived plants have stronger demographic
responses to climate. Nature Communications. Nature Communications. DOI:
10.1038/s41467-021-21977-9

\textbf{Levin SC}, Crandall RM, Pokoski TC\(^\ast\), Stein C \& Knight
TM (2020). Phylogenetic and functional distinctiveness explain alien
plant population responses to competition. Proceedings of the Royal
Society B. DOI: 10.1098/rspb.2020.1070

Sandel B, Weigelt P, Kreft H, Keppel G, van der Sande MT, \textbf{Levin
SC}, Smith S, Craven DC \& Knight TM (2019). Current climate, isolation,
and history drive global patterns of tree phylogenetic endemism. Global
Ecology and Biogeography. DOI: 10.1111/geb.13001

Compagnoni A, Bibian BJ, Ochocki BM, \textbf{Levin SC}, Zhu K \& Miller
TEX (2019). popler: an R package for extraction and synthesis of
population time series from the long-term ecological research (LTER)
network. Methods in Ecology and Evolution. DOI: 10.1111/2041-210X.13319

\textbf{Levin SC}, Crandall RM, Knight TM (2019) Population projection
models for 14 alien plant species in the presence and absence of
above‐ground competition. Ecology. DOI: 10.1002/ecy.2681

Carl G, \textbf{Levin SC}, Kühn I. (2018) spind: an R Package to Account
for Spatial Autocorrelation in the Analysis of Lattice Data.
Biodiversity Data Journal. DOI: 10.3897/BDJ.6.e20760

\hypertarget{workshops-invited-talks}{%
\subsection{Workshops \& Invited Talks}\label{workshops-invited-talks}}

\textbf{Levin SC}, Childs DZ, Compagnoni AC, Evers S, Knight TM \&
Salguero-Gomez R. \texttt{ipmr}: An R Package for Easy and Flexible
Construction and Interpretation of Integral Projection Models.
Ecological Society of America, Long Beach, August 2021.

\textbf{Levin SC}. Invasive plants: research, control, and what you can
do to help! Point Reyes National Park, May 2020. (Cancelled due to
COVID-19 pandemic).

\textbf{Levin SC} \& Salguero-Gomez R. Effective, efficient, and safe
data collection with UAVs. Oxford University, January 2020.

Salguero-Gomez R, Jones OR, \emph{et al.} A gentle introduction to the
COMADRE \& COMPADRE databases for demographic analyses. British
Ecological Society, Belfast, December 2019.

\hypertarget{presentations}{%
\subsection{Presentations}\label{presentations}}

\(^\ast\) \emph{denotes mentee; \(^\#\) denotes poster presentations,
otherwise oral}

\textbf{2020}

Salguero-Gomez R,Che-Castaldo JP, Jones O, Caswell H, Ezard T,
Hernandez-Yanez H, Hodgson D, Knight TM, \textbf{Levin SC}, Stott I,
Thomas C, Vaupel J. (2020) The next generation of demographic databases:
Building and delivering a distributed network for user contributions and
engagement. Ecological Society of America

\textbf{2018}

\textbf{Levin SC}, RM Crandall, TC Pokoski, Stein C, Knight TM.
Mechanisms underlying the differential success of alien plant species.
Ecological Society of America -- New Orleans, USA

\textbf{2016}

\textbf{Levin SC}, Stein C, Knight TM. Phylogenetic novelty alters the
strength of biotic interactions for exotic plant species. NeoBiota 2016
-- Vianden, Luxembourg

\textbf{Levin SC}, Stein C, Knight TM. Phylogenetic novelty alters the
strength of biotic interactions for exotic plant species. iDiv
Conference -- Leipzig, Germany

\textbf{2015}

Poor E\(^\ast\),Thompson AH\(^\ast\), \textbf{Levin SC}, Knight TM.
Novel functional traits aid the success of the invasive biennial Carduus
nutans. Washington University in St.~Louis Undergraduate Research
Symposium -- St.~Louis, MO \(^\#\)

Workman M\(^\ast\), Thompson AH\(^\ast\), \textbf{Levin SC}, Knight TM.
Competitive release may increase the fitness of exotic plants in their
novel range. Washington University in St.~Louis Undergraduate Research
Symposium -- St.~Louis, MO \(^\#\)

\textbf{2014}

Patterson A\(^\ast\), Galluppi CG, \textbf{Levin SC}, Maynard EE, Knight
TM. How plant species become common: examining the success strategies of
native and invasive plants. Washington University in St.~Louis
Undergraduate Research Symposium -- St.~Louis, MO \(^\#\)

Van Horn T\(^\ast\), Galluppi CG, \textbf{Levin SC}, Knight TM.
Examining the enemy release hypothesis in Ozark woody species.
Washington University in St.~Louis Undergraduate Research Symposium --
St.~Louis, MO \(^\#\)

\hypertarget{software}{%
\section{Software}\label{software}}

Maintainer (current) and developer (\textgreater{} v2.0.0) of
\emph{spind}. \href{https://github.com/levisc8/spind}{Project page} and
\href{https://cran.r-project.org/package=spind}{CRAN}

Maintainer and developer of \emph{ipmr}.
\href{https://levisc8.github.io/ipmr/}{Project page} and
\href{https://cran.r-project.org/package=ipmr}{CRAN}

Maintainer and developer of the \emph{Padrino IPM Database} and
\emph{Rpadrino}. \href{https://levisc8.github.io/Padrino/}{Project
page}.

Contributed to development of
\href{https://github.com/AldoCompagnoni/popler}{popler},
\href{https://github.com/EduardoArle/bRacatus}{bRacatus},
\href{https://github.com/valentinitnelav/plotbiomes}{plotbiomes},
\href{https://github.com/iainmstott/popdemo}{popdemo},
\href{https://github.com/jonesor/Rcompadre}{Rcompadre}, and
\href{https://github.com/jonesor/Rage}{Rage}.

\hypertarget{languages}{%
\section{Languages}\label{languages}}

Fluent in English and R, proficient with Stan, Git, and C++, and
familiar with Python and German.

\hypertarget{certifications}{%
\section{Certifications}\label{certifications}}

United States FAA Part 107 UAV Pilot License

United States NPS S212 A Faller

\hypertarget{mentoring}{%
\section{Mentoring}\label{mentoring}}

Sanne Evers \hfill Helmholtz-Zentrum für Umweltforschung

Ana Bogdan \hfill Babe\c s-Bolyai University, Cluj-Napoca, Romania

Tyler Pokoski \hfill  University of Iowa 2017

Tom Collins \hfill Missouri S\&T 2017

Amy Patterson \hfill Washington University in St.~Louis 2015

Amibeth Thompson \hfill Illinois College 2014

Sami Hunkler \hfill University of California, Berkeley 2017

Thomas Van Horn \hfill Washington University in St.~Louis 2018

Sarah Link \hfill Eureka High School 2015

Brenda Alvarado \hfill Francis Howell North 2015

Matilda Workman \hfill Kirkwood High School 2017

Elizabeth Poor \hfill Clayton High School 2017

\hypertarget{service}{%
\section{Service}\label{service}}

Reviewer for rOpenSci, BMC Ecology, Annals of Botany, and Plant Ecology

\hypertarget{referees}{%
\section{Referees}\label{referees}}

\textbf{Dr.~Tiffany Knight}

Martin Luther University, Helmholtz-Zentrum für Umweltforschung, German
Centre for Integrative Biodiversity

\href{mailto:tiffany.knight@idiv.de}{\nolinkurl{tiffany.knight@idiv.de}}

\textbf{Dr.~Roberto Salguero-Gomez}

Oxford University Department of Zoology

\href{mailto:rob.salguero@zoo.ox.ac.uk}{\nolinkurl{rob.salguero@zoo.ox.ac.uk}}

\end{document}
